Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-02-08 Manuscript1.Rmd
Manuscript update

# Discussion
-	The disturbance significantly impact the functional and taxonomic composition and diversity of the stands for more than 30 years 
-	Important differences among plots of same treatments: possible impact of initial diversity composition, local abiotic parameters (topography, soils, surrounding stands).   Impacts depend on the disturbance intensity, but further parameters may be involved. 
-	The shift in functional composition differs from the null model: biotic and abiotic filters are at stake but only tangible from 10/15 years after logging. Discussion with Cannon, 1998: they found no different process than rarefaction for 8 years after logging, but the time might have been too short-> divergence due to recruitment and not rarefaction after random species disappearance. Same conclusions otherwise.
-	Disturbance involves new filters for species settling in the stands, probably according to their functional strategy. Disturbance generates a functional shift of communities toward acquisitive strategies. Ecosystems function rely on abundant species: changes in stands functioning is then expected.  (Flores, 2006  for differential sapling success after disturbance).
-	If the recovery is not achieved 30 years after disturbance, it is on the way to. Only one plot displayed a still increasing Simpson diversity, and all plots showed a stabilization or a decrease of the composition distancing from 1989 inventories. however this is the impact of a single disturbance event: the repetition may have different impact (@Olander2005 demonstrated the impact of logging on soils nutrient and compaction)
-	To go further we should focus on recruitment which would also highlight the mechanisms underlying these shifts and dynamics and explicit the environmental filter.

>>>>

# Discussion
-	The disturbance significantly impact the functional and taxonomic composition and diversity of the stands for more than 30 years. 
< Question Hubbel vs. Molino: IDH or not, if the composition is affected the changes are oriented then the IDH is valid. >
-	Important differences among plots of same treatments: possible impact of initial diversity composition, local abiotic parameters (topography, soils, surrounding stands).   Impacts depend on the disturbance intensity, but further parameters may be involved. 
-	The shift in functional composition differs from the null model: biotic and abiotic filters are at stake but only tangible from 10/15 years after logging. Discussion with Cannon, 1998: they found no different process than rarefaction for 8 years after logging, but the time might have been too short-> divergence due to recruitment and not rarefaction after random species disappearance. Same conclusions otherwise.
-	Disturbance involves new filters for species settling in the stands, probably according to their functional strategy. Disturbance generates a functional shift of communities toward acquisitive strategies. Ecosystems function rely on abundant species: changes in stands functioning is then expected.  (Flores, 2006  for differential sapling success after disturbance).
-	If the recovery is not achieved 30 years after disturbance, it is on the way to. Only one plot displayed a still increasing Simpson diversity, and all plots showed a stabilization or a decrease of the composition distancing from 1989 inventories. however this is the impact of a single disturbance event: the repetition may have different impact (@Olander2005 demonstrated the impact of logging on soils nutrient and compaction)
-	To go further we should focus on recruitment which would also highlight the mechanisms underlying these shifts and dynamics and explicit the environmental filter.
